A Case Study on Abstractions to Converge High-Throughput and High-Performance Computing

### 2017-03-21 overall.tex
Backfill availability 2016 plot and iteration in V

Figure~\ref{fig:backfill-distrib} shows the distribution of backfill
availability on Titan as a function of number of nodes and the time of their
availability (i.e., walltime). We recorded these data by polling Titan's Moab
scheduler at regular intervals between Oct 28 and Nov 3 2015, while developing
PanDA Broker. The mean number of nodes was 267.1, and their mean walltime was
1445 minutes. Detector simulations of 100 events, enable to use down to 1 node
for 1/4 of the mean walltime of backfill availability. As such, it offers a good
compromise for PanDA Broker efficiency.

\begin{figure}[htp]
    \includegraphics[clip,width=\columnwidth]{figures/avail_time_vs_nodes_Oct_28_Nov_3_2015.pdf}
    \caption{Backfill availability measures as walltime vs number of cores
    between Oct 28 and Nov 2015. Availability was measured 5312 times: mean
    number of work nodes available 267.1; mean walltime available 1445
    minutes.\mtnote{Waiting to know whether we have data for the experiment
    time window.}}
\label{fig:backfill-distrib}
\end{figure}

>>>>

Figure~\ref{fig:backfill-distrib} shows the distribution of backfill
availability on Titan as a function of number of nodes and the time of their
availability (i.e., walltime). We recorded these data by polling Titan's Moab
scheduler at regular intervals during the experiment window time, while
developing and deploying PanDA Brokers. The mean number of nodes was 680, and
their mean walltime was 680 minutes. Detector simulations of 100 events, enable
to use down to 1 node for 1/2 of the mean walltime of backfill availability. As
such, it offers a good compromise for PanDA Broker efficiency.

\begin{figure}[htp]
    \includegraphics[clip,width=\columnwidth]{figures/titan_backfill_avail.pdf}
    %figures/avail_time_vs_nodes_Oct_28_Nov_3_2015.pdf}
    \caption{Backfill availability measures as walltime in minutes vs number of
    work nodes during the experiment window time. Availability was measured
    62175 times: mean number of work nodes available 680; mean walltime
    available 680 minutes.}
\label{fig:backfill-distrib}
\end{figure}
